---
title: "TestReport"
output: html_document
params:
  df: NULL
  biggest_5_column_names: NULL
  biggest_5_column_values: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(ggplot2)
library(reactable)
library(dplyr)
```


## Executive Summary

This report provides an analysis of the aggregated data based on your selected category and measure.

---

## Top 5 Results

The table below shows the top 5 entries based on the selected aggregation:
```{r top5_table}
if (!is.null(params$biggest_5_column_names) && !is.null(params$biggest_5_column_values)) {
  top5_df <- data.frame(
    Category = params$biggest_5_column_names,
    Value = params$biggest_5_column_values
  )
  
  # Check output format
  if (knitr::is_html_output()) {
    # Use reactable for HTML
    reactable(
      top5_df,
      striped = TRUE,
      highlight = TRUE,
      bordered = TRUE,
      showPageSizeOptions = TRUE,
      filterable = TRUE,
      theme = reactableTheme(
        color = "hsl(233, 9%, 87%)",
        backgroundColor = "hsl(233, 9%, 19%)",
        borderColor = "hsl(233, 9%, 22%)",
        stripedColor = "hsl(233, 12%, 22%)",
        highlightColor = "hsl(233, 12%, 24%)",
        inputStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
        selectStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
        pageButtonHoverStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
        pageButtonActiveStyle = list(backgroundColor = "hsl(233, 9%, 28%)")
      )
    )
  } else {
   flextable(top5_df) |> 
    bold(part = "header")
  }
} else {
  print("No data available for top 5 results.")
}
```


---

## Visualization
```{r top5_chart, fig.width=10, fig.height=6}
if (!is.null(params$biggest_5_column_names) && !is.null(params$biggest_5_column_values)) {
  top5_df <- data.frame(
    Category = params$biggest_5_column_names,
    Value = params$biggest_5_column_values
  )
  
  ggplot(top5_df, aes(x = reorder(Category, Value), y = Value)) +
    geom_col(fill = "#3498db", alpha = 0.8) +
    geom_text(aes(label = round(Value, 2)), hjust = -0.2, size = 4) +
    coord_flip() +
    labs(
      title = "Top 5 Categories by Value",
      x = "Category",
      y = "Value"
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 16, face = "bold"),
      axis.title = element_text(size = 12),
      axis.text = element_text(size = 10)
    )
} else {
  print("No data available for visualization.")
}
```



---


## Report Information

- **Generated:** `r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`
- **Total Records:** `r if(!is.null(params$df)) nrow(params$df) else 0`
- **Columns:** `r if(!is.null(params$df)) paste(names(params$df), collapse = ", ") else "N/A"`